---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
# hw07-katiezinn
hw07-katiezinn created by GitHub Classroom

Welcome to my 7th homework assignment! For this assignment I added created a package that allows us to calculate the instantaneous growth of fish.

# What did I do?
For this assignment I creating a package with a usefu function called `instantaneous_growth()`

[![Build Status](https://travis-ci.org/vincenzocoia/powers.svg?branch=master)](https://travis-ci.org/katiezinn/growth-master/)

__Note__: This R package is not mean to be "serious". It's just for teaching purposes. 

# Powers

This is an R package that gives `sqrt()` friends by providing other power functions.

## Installation

You can install powers from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("katiezinn/powers")
```

## Example

See the vignette for more extensive use, but here's an example:

```{r example}
powers::reciprocal(2)
```

## For Developers

(Again, I don't actually intend for anyone to develop this silly package, but if I did, here's what I'd write.)

Use the internal `pow` function as the machinery for the front-end functions such as `square`, `cube`, and `reciprocal`. 
